---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# demodel

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/CChen89/demodel.svg?branch=main)](https://travis-ci.com/CChen89/demodel)
[![R-CMD-check](https://github.com/CChen89/demodel/workflows/R-CMD-check/badge.svg)](https://github.com/CChen89/demodel/actions)
<!-- badges: end -->

The goal of demodel is to provide user-friendly functionality for early phase dose finding trial. This package will be updated for more models.

## Installation

You can install the released version of demodel from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("demodel")
```

## Example

This is a basic example which shows you how to fit early phase trial data:

```{r example}
library(demodel)
# design info ----------------------------------------------------------------------------

MB.Info <- MBInfo(dose.levels = list(DSPX = c(80, 120, 160, 200, 240, 280)),
                  ref.dose = 120,
                  bounds = c(0.16, 0.33),
                  ewoc = 0.25,
                  trial.name = "DSP-509",
                  drug.name = "DSP509",
                  drug.unit = "mg")

# Bayes Info ---------------------------------------------------------------------------

Bayes.Info <- BayesInfo(MCMCpackage = "rjags",
                        prior = list(mean = list(c(-1.7346, 0)), std = list(c(2, 1)), corr = list(0)),
                        init.list = list(list(paras1 = c(-3, 0), .RNG.seed = 1, .RNG.name="base::Wichmann-Hill"),
                                         list(paras1 = c(-3, 0), .RNG.seed = 2, .RNG.name="base::Wichmann-Hill")),
                        n.sample = 10000,
                        n.burn = 2000,
                        n.adapt = 1000,
                        n.chain = 2,
                        n.thin = 1)

 demodel_mono <- demodelFit(data = blrm_mono_data,
                            formula = cbind(nDLT, npat) ~ DSPX,
                            method = "blrm",
                            mbdInfo = MB.Info,
                            bayesInfo = Bayes.Info,
                            multiSce = ~ Scenario,
                            control = demodelControl(code.name = "demodel_core.R",
                                                     output.path = NULL, # change to getwd() if require a report
                                                     table.file.name = NULL, # provide a file name if require a report
                                                     fig.file.name = NULL))
```

This results in a summary using tables  

```{r table names}
names(demodel_mono$res.summary)
```

and a summary using figures

```{r figures, fig.width=20, fig.width=18}
names(demodel_mono$plot.summary)
```

To be continue
